A Switching Planner for Combined Task and Observation Planning

### 2010-11-19 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
Completed the Hoffman+palacios thread... I could not bring myself to move forward on this until I had, as in my mind it is _hugely_ related
 - Charles

%%
Recently the systems
\system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009}, demonstrated how conformant
planning ---i.e., serial planning in unobservable worlds--- can be
modelled as a deterministic problem, and therefore solved using serial
systems. In this conformant setting, advances have been towards
compact representations and lazy evaluations of beliefs.

>>>>

%%
Recently the systems
\system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009}, demonstrated how conformant
planning ---i.e., serial planning in unobservable worlds--- can be
modelled as a deterministic problem, and therefore solved using serial
systems. In this conformant setting, advances have been towards
compact representations of beliefs amenable to existing best-first
search planning procedures, and lazy evaluations of beliefs. This
research thread has also been extended recently to contingent planning
in fully observable non-deterministic
environments~\cite{albore:etal:2009}.
